---
title: "Midterm"
format: html
---

Student's t distribution is widely used in many areas of statistics. For $\nu$ degrees of freedom, the probability density function is given by the following: 

$$
f(x)=\frac{\Gamma(\frac{\nu+1}{2})}{\sqrt{\pi\nu}\Gamma(\frac\nu 2)}(1+\frac{x^2}{\nu})^{-\frac{\nu+1}{2}}; \quad x\in(-\infty,\infty)
$$


1. Create a function in R called `my_dt` to calculate $f(x)$ at a given $x$ and $\nu$. (Hint: the `gamma()` function will be useful here)

```{r}
#| eval: false
#| include: true
my_dt <- function(x, nu) {
  fx <- "FUNCTION HERE"
  return(fx)
}
```

2. R has a built in t distribution density function, `dt()`, that you can use to verify your solution to (1). Evaluate both your function and `dt()` at the following values of x and $\nu$ and arrange your results into a neatly formatted table.

    - $x=-1.5, \nu=6$
    - $x=0.7, \nu=20$
    - $x=2, \nu=4$

```{r}
#| include: false
set.seed(380)
y <- rnorm(30, 2, 3)
dput(round(y,1))
```

3. A sample of 30 data points was collected and provided below. Calculate the t-statistic of the mean using $t=\frac{\bar{X}}{s/\sqrt n}$, where $\bar{X}$ is the sample mean, $s$ is the sample standard deviation, and $n$ is the sample size.

```{r}
y <- c(2.7, 2, 0.1, 8.2, -1.2, -3.8, -0.2, 3.6, 0.3, 3.1, 2.7, 3.4, 
-0.8, 0.4, 2.1, -2.3, 3.9, 0.1, 4.4, 0.8, 3.1, -0.4, 5.2, 2.2, 
0, 2.6, -0.3, -3.9, -0.5, -2.5)
```

4. Using `my_dt`, compute $P(X\leq -|t|)+P(X \geq |t|)$ for $\nu=29$. (Hint: the `integrate` function will be helpful here, as well as the `Inf` object)

5. Run the following line and compare the p-value with your result from (4). 

```{r}
t.test(y)
```

6. In 2-4 sentences, describe what is represented by $1-P(-t\leq x \leq t)$. 







